Sampling in Decisions from Experience

### 2021-10-08 slides_modelers-meeting.Rmd
Move document to main directory

---
title: "Sampling in Decisions from Experience"
subtitle: https://github.com/linushof/sampling-in-dfe
author: "Linus, Veronika & Thorsten"
date: "October 11, 2021"
output:
  beamer_presentation: default
bibliography: references_sampling-in-dfe.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

pacman::p_load(tidyverse, 
               scico)
```

@@

## plot curves
cpt_w %>% 
  filter(a != 1) %>% 
  group_by(boundary, a, s) %>% 
  ggplot(aes(x = ep, y = w, color = s)) +
  geom_path(size = 1.2) + 
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) + 
  labs(title = "Probability Weighting Function",
       x ="Experienced Probability",
       y = "Subjective Experienced Probability", 
       color="Switching Probability") + 
  theme_minimal()
```

>>>>

---
title: "Sampling in Decisions from Experience"
subtitle: https://github.com/linushof/sampling-in-dfe
author: "Linus, Veronika & Thorsten"
date: "October 11, 2021"
output:
  beamer_presentation: default
bibliography: references_sampling-in-dfe.bib
csl: apa.csl
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, 
               scico,
               gridExtra)
```

@@

## plot curves
curve <- cpt_w %>% 
  group_by(boundary, a, s) %>% 
  ggplot(aes(x = ep, y = w, color = s)) +
  geom_path(size = 1.1) + 
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) +
  scale_y_continuous(breaks = seq(0, 1, .1)) + 
  labs(x ="Experienced Probability",
       y = "Subjective Experienced Probability", 
       color="Switching Probability") + 
  theme_minimal()

gamma <- cpt %>% 
  group_by(boundary, a) %>% 
  ggplot(aes(x = s, y = gamma, color = s)) +
  geom_jitter(size = 3, show.legend = FALSE) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(breaks = seq(0, 2, .2)) +
  labs(title = expression(paste("Curvature ", gamma)),
       x ="Switching Probability",
       y = expression(gamma), 
       color="Switching Probability") + 
  theme_minimal()

delta <- cpt %>% 
  ggplot(aes(x = s, y = delta, color = s)) +
  geom_jitter(size = 3, show.legend = FALSE) +
  scale_color_scico(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(limits = c(0.75, 2.25), breaks = seq(0.75, 2.25, .25)) +
  labs(title = expression(paste("Elevation ", delta)),
       x ="Switching Probability",
       y = expression(delta), 
       color="Switching Probability") + 
  theme_minimal()

plot_params <- grid.arrange(gamma, delta, nrow = 2)

grid.arrange(plot_params, curve, nrow = 1)
```
